Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-29 dit-paper_ieee.tex
- small changes
- ilovetabs.gif

	The \emph{C-space} of a real-time system is, intuitively,
	the set of WCET values for which this system would be feasible. A
	precise and efficient description of its C-space would allow to quickly decide
	if a system is feasible on a given platform.\\

@@

  The description we presented in Section \ref{sct:cspaceDescr} was general, and is thus still relevant. Therefore the C-space is still accurately described by the following infinite number of constraints:$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$

@@

\subsubsection{Job arrival and deadline}

Consider an interval $[t_1, t_2]$. If $t_2$ is an instant without any job deadline, then by definition the value of $\dbf{t_1, t_2}$ will be equal to $\dbf{t_1, t_2^*}$, where $t_2^*$ is the latest deadline before $t_2$.\\

@@

  \subsubsection{Feasibility interval}

  First let us recall how an asynchronous system behaves under an optimal scheduler, for example EDF.\\

>>>>

	The \emph{C-space} of a real-time system is, intuitively,
	the set of WCET values for which this system would be feasible. A
	precise and efficient description of its C-space would allow to quickly decide
	whether or not a system is feasible on a given platform.\\

@@

		The description we presented in Section \ref{sct:cspaceDescr} was general, and
		is thus still relevant. Therefore the C-space is still accurately described by
		the following infinite number of constraints:

		\[
			\sum_{i=0}^{n-1} n_i(t_1, t_2)
			\, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\]

@@

		\subsubsection{Job arrival and deadline}
			Consider an interval $[t_1, t_2]$. If $t_2$ is an instant without any job
			deadline, then by definition the value of $\dbf{t_1, t_2}$ will be equal to
			$\dbf{t_1, t_2^*}$, where $t_2^*$ is the latest deadline before $t_2$.\\

@@

		\subsubsection{Feasibility interval}
			First let us recall how an asynchronous system behaves under an optimal
			scheduler, for example EDF.\\
